MLH1 Results Outline

### 2020-03-06 doc/Results.rmd
adding more interference notes

table <- raw.gamma_estimates
write.table(table, "~./MLH1repo/table.csv", sep=",",row.names = TRUE)

write.table(summarize_rbar_table, "~./MLH1repo/RBAR.table.csv", sep=",",row.names = TRUE)

@@

>>>>

table <- raw.gamma_estimates
#write.table(table, "~./MLH1repo/table.csv", sep=",",row.names = TRUE)

#write.table(summarize_rbar_table, "~./MLH1repo/RBAR.table.csv", sep=",",row.names = TRUE)

@@

#this plot shows much higher 2CO interference (via the gamma estimat from nrmIFD) in high rec males
#across other classes of bivalents

#most all other estiamtes of gamma estimates are around 4
#

#house mouse raw nu is around 11
